Quickie for importing tasks to OmniFocus 3

### 2022-04-02 _posts/2022-04-02-quickie-for-importing-tasks-to-omnifocus-3/quickie-for-importing-tasks-to-omnifocus-3.Rmd
typos

Well, sort of. I used it a ton in version 1.0 and then eventually stopped. Then I used it again a ton wehen version 2 came out, and then eventually stopped. It worked well when I really forced myself to use it, but eventually I'd run out of gas, and it always bugged me a bit that I couldn't get a handle on why. I read David Allen's "[Getting Things Done](https://gettingthingsdone.com/)", which it was inspired by, and it all made sense, but it still just had a lot of friction to keep using.

One of the problems, I now realize, was the notion of *contexts* - each to-do list could be assigned one, *and only one*, context, like "online" or "supermarket" or "home", describing the setting where a task could be done. The problem was that there were many tasks that could be done in multiple contexts, but no way to mark them as such. One user I talked with on one of the forums explained that the way to think about it was that I myself could be in multiple simultaneous contexts, like "home" and "online", and that tasks that matched either of those would appear. It sort of made sense, but it still never felt natural and I eventually dropped it again.

@@

```
- (ch 3) Simple linear regression @tags(Machine Learning, Homework) @projects(Machine Learning) @due(2022-04-02 23:59)
- (ch 3) Multiple linear regression @tags(Machine Learning, Homework) @due(2022-04-03 23:59)
- (ch 4) Logistic regression @tags(Machine Learning, Homework) @due(2022-04-04 23:59)
- (ch 4) Multiple logistic regression @tags(Machine Learning, Homework) @due(2022-04-05 23:59)
- (ch 4) Linear discriminant analysis @tags(Machine Learning, Homework) @due(2022-04-06 23:59)
- (ch 4) Quadratic discriminant analysis @tags(Machine Learning, Homework) @due(2022-04-07 23:59)
- (ch 4) Naive Bayes @tags(Machine Learning, Homework) @due(2022-04-08 23:59)
- (ch 4) K-Nearest Neighbors @tags(Machine Learning, Homework) @due(2022-04-09 23:59)
- (ch 4) Poisson regression @tags(Machine Learning, Homework) @due(2022-04-10 23:59)
- (ch 5) Cross-validation @tags(Machine Learning, Homework) @due(2022-04-11 23:59)
- (ch 5) Bootstrap @tags(Machine Learning, Homework) @due(2022-04-12 23:59)
- (ch 6) Best subset selection @tags(Machine Learning, Homework) @due(2022-04-13 23:59)
- (ch 6) Stepwise selection @tags(Machine Learning, Homework) @due(2022-04-14 23:59)
- (ch 6) Ridge regression @tags(Machine Learning, Homework) @due(2022-04-15 23:59)
- (ch 6) Lasso @tags(Machine Learning, Homework) @due(2022-04-16 23:59)
- (ch 6) Principal component regression @tags(Machine Learning, Homework) @due(2022-04-17 23:59)
- (ch 8) Bagging @tags(Machine Learning, Homework) @due(2022-04-18 23:59)
- (ch 8) Random forests @tags(Machine Learning, Homework) @due(2022-04-19 23:59)
- (ch 8) Boosting @tags(Machine Learning, Homework) @due(2022-04-20 23:59)
- (ch 8) Bayesian Additive Regression Trees @tags(Machine Learning, Homework) @due(2022-04-21 23:59)
- (ch 9) Support Vector Machines @tags(Machine Learning, Homework) @due(2022-04-22 23:59)
- (ch 12) Principal component analysis @tags(Machine Learning, Homework) @due(2022-04-23 23:59)
- (ch 12) K-means clustering @tags(Machine Learning, Homework) @due(2022-04-24 23:59)
- (ch 12) Hierarchical clustering @tags(Machine Learning, Homework) @due(2022-04-25 23:59)
```

>>>>

Well, sort of. I used it a ton in version 1.0 and then eventually stopped. Then I used it again a ton when version 2 came out, and then eventually stopped. It worked well when I really forced myself to use it, but eventually I'd run out of gas, and it always bugged me a bit that I couldn't get a handle on why. I read David Allen's "[Getting Things Done](https://gettingthingsdone.com/)", which it was inspired by, and it all made sense, but it still just had a lot of friction to keep using.

One of the problems, I now realize, was the notion of *contexts* - each to-do item could be assigned to one, *and only one*, context, like "online" or "supermarket" or "home", describing the setting where a task could be done. The problem was that there were many tasks that could be done in multiple contexts, but no way to mark them as such. One user I talked with on one of the forums explained that the way to think about it was that I myself could be in multiple simultaneous contexts, like "home" and "online", and that tasks that matched either of those would appear. It sort of made sense, but it still never felt natural and I eventually dropped it again.

@@

```
- (ch 3) Simple linear regression @tags(Machine Learning, Homework) @due(2022-04-02 23:59)
- (ch 3) Multiple linear regression @tags(Machine Learning, Homework) @due(2022-04-03 23:59)
- (ch 4) Logistic regression @tags(Machine Learning, Homework) @due(2022-04-04 23:59)
- (ch 4) Multiple logistic regression @tags(Machine Learning, Homework) @due(2022-04-05 23:59)
- (ch 4) Linear discriminant analysis @tags(Machine Learning, Homework) @due(2022-04-06 23:59)
- (ch 4) Quadratic discriminant analysis @tags(Machine Learning, Homework) @due(2022-04-07 23:59)
- (ch 4) Naive Bayes @tags(Machine Learning, Homework) @due(2022-04-08 23:59)
- (ch 4) K-Nearest Neighbors @tags(Machine Learning, Homework) @due(2022-04-09 23:59)
- (ch 4) Poisson regression @tags(Machine Learning, Homework) @due(2022-04-10 23:59)
- (ch 5) Cross-validation @tags(Machine Learning, Homework) @due(2022-04-11 23:59)
- (ch 5) Bootstrap @tags(Machine Learning, Homework) @due(2022-04-12 23:59)
- (ch 6) Best subset selection @tags(Machine Learning, Homework) @due(2022-04-13 23:59)
- (ch 6) Stepwise selection @tags(Machine Learning, Homework) @due(2022-04-14 23:59)
- (ch 6) Ridge regression @tags(Machine Learning, Homework) @due(2022-04-15 23:59)
- (ch 6) Lasso @tags(Machine Learning, Homework) @due(2022-04-16 23:59)
- (ch 6) Principal component regression @tags(Machine Learning, Homework) @due(2022-04-17 23:59)
- (ch 8) Bagging @tags(Machine Learning, Homework) @due(2022-04-18 23:59)
- (ch 8) Random forests @tags(Machine Learning, Homework) @due(2022-04-19 23:59)
- (ch 8) Boosting @tags(Machine Learning, Homework) @due(2022-04-20 23:59)
- (ch 8) Bayesian Additive Regression Trees @tags(Machine Learning, Homework) @due(2022-04-21 23:59)
- (ch 9) Support Vector Machines @tags(Machine Learning, Homework) @due(2022-04-22 23:59)
- (ch 12) Principal component analysis @tags(Machine Learning, Homework) @due(2022-04-23 23:59)
- (ch 12) K-means clustering @tags(Machine Learning, Homework) @due(2022-04-24 23:59)
- (ch 12) Hierarchical clustering @tags(Machine Learning, Homework) @due(2022-04-25 23:59)
```
